Structural Divergence Analysis

### 2016-12-11 analysis-structure3-core.Rmd
cambios 2 11/12/16

```{r_comparison_mean_z.RSD_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
# comparison of z.RSD profiles
ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset)) +
  geom_line() +
  geom_text(data = subset(d, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8)+
  geom_vline(xintercept = active.sites, show.legend = F) +
  geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) + 
  scale_colour_manual(name = NULL, values = myColors)

@@

knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")
```

### Distances to the active sites

```{r_comparison_da}

```

```{r_comparison_vs_plots}

@@

plot(x = d.exp$mean.z.RSD, 
     y = d.mut$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "mut.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.mut$mean.z.RSD)[active.sites], col = "yellow")
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], col = "green")
abline(0, 1)

plot(x = d.exp$mean.z.RSD, 
     y = d.strong$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "strong.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)

plot(x = d.mut$mean.z.RSD, 
     y = d.strong$mean.z.RSD, 
     xlab = "mut.mean.z.RSD", 
     ylab = "strong.mean.z.RSD", 
     xlim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))),
     ylim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))))
points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)
```

>>>>

```{r_comparison_mean_z.RSD_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}

@@

knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")

@@

plot(x = d.exp$mean.z.RSD, 
     y = d.mut$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "mut.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
abline(0, 1)

plot(x = d.exp$mean.z.RSD, 
     y = d.strong$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "strong.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))))
abline(0, 1)

plot(x = d.mut$mean.z.RSD, 
     y = d.strong$mean.z.RSD, 
     xlab = "mut.mean.z.RSD", 
     ylab = "strong.mean.z.RSD", 
     xlim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))),
     ylim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))))
abline(0, 1)
```
